Contention Management for 5G

### 2017-04-19 article/article.tex
eojv

    \subsubsection{Results}
      The following performance evaluation results compares the previous algorithms. Since we try to find a polynomial time algorithm for the problem PALL, Exhaustive Generation is not a good solution. However, Greedy 3NT and Shortest-Longest are some greedy heuristics and gives us a polynomial complexity. We tried to determine which algorithm gives a solution with the minimal period.
      In a first time, we will have a look at the results with the parameters corresponding to Cloud-RAN context.
      \paragraph{Short routes}
      To correspond with the C-RAN applications, we made some simulations on graphs in which $\lambda(c_s,r_{s_i})$ and $\lambda(c_t,r_{t_i})$, are drawn following an uniform act between 0 and 700 slots, that is, at the most, 5 km between the RRH and its BBU. The messages size $\tau$ is to 2500 slots, that is, approximately 1.228 Gbps of data for each route. The size of a slot is given by the time taken to send 64 bytes on the network, in which the links has 10Gbps throughput.

@@

      With those parameters, we can observe that the average period of the Shortest-Longest algorithm, which is determined by the difference between the longest and the shortest route, is always equal to the Exhaustive generation, that is, the lower bound.
      The next results is to theoretically prove that, with those parameters, the Shortest-Longest algorithm gives optimal solutions, like this experimental study suggests it does. 
      About the Greedy 3NT Algorithm, with those parameters, it always gives us bigger periods than the Shortest longest. 
      We can also observe that, for any algorithm, the average minimal periods increases linearly with the number of routes. Thus, the following experiences are made on a fixed number of routes : 8.

@@

      One the other hand, one can imagine that the greedy $3n\tau$ algorithm finds reasonable solutions, because the algorithm does not consider the size of the route, and thus, is not impacted by this parameter.
       \begin{center}
      \includegraphics[scale=0.4]{echec_longues.pdf}
      \end{center}

@@

On $c_t$, the policy is the following one, after setting the clock to 0:
\begin{enumerate}
 \item To be eligible, a job needs to be able to come back on the switch at the current clock (if clock = 0, take the first message able to come back).
 \item Between the eligible jobs, schedule first the one which has the longest route and gives it the offset time $m_{\cal C(s_i)} = clock$.
 \item Update the clock at the time in which the scheduled task is over: $$clock = clock + message\ length$$.
\end{enumerate}

@@

	\paragraph{Algorithm}
	\paragraph{Analysis}

>>>>

    \subsubsection{Results}
      The following performance evaluation results compares the previous algorithms. Since we try to find a polynomial time algorithm for the problem PALL, Exhaustive Generation is not a good solution. However, Greedy $3.n.\tau$ and Shortest-Longest are some greedy heuristics and gives us a polynomial complexity. We tried to determine which algorithm gives a solution with the minimal period.
      In a first time, we will have a look at the results with the parameters corresponding to Cloud-RAN context.
      \paragraph{Short routes}
      To correspond with the C-RAN applications, we made some simulations on graphs in which $\lambda(c_s,r_{s_i})$ and $\lambda(c_t,r_{t_i})$, are drawn following an uniform act between 0 and 700 slots, that is, at the most, 5 km between the RRH and its BBU. The messages size $\tau$ is to 2500 slots, that is, approximately 1.228 Gbps of data for each route. The size of a slot is given by the time taken to send 64 bytes on the network, in which the links has 10Gbps throughput.

@@

      With those parameters, we can observe that the average period of the Shortest-Longest algorithm, which is determined by the difference between the longest and the shortest route, is always equal to the Exhaustive generation, that is, the lower bound.
      The next results is to theoretically prove that, with those parameters, the Shortest-Longest algorithm gives optimal solutions, like this experimental study suggests it does. 
      About the Greedy $3.n.\tau$ Algorithm, with those parameters, it always gives us bigger periods than the Shortest longest. 
      We can also observe that, for any algorithm, the average minimal periods increases linearly with the number of routes. Thus, the following experiences are made on a fixed number of routes : 8.

@@

      One the other hand, one can imagine that the greedy $3.n.\tau$ algorithm finds reasonable solutions, because the algorithm does not consider the size of the route, and thus, is not impacted by this parameter.
       \begin{center}
      \includegraphics[scale=0.4]{echec_longues.pdf}
      \end{center}

@@

On $c_t$, the policy is the following one, after setting the clock to 0:
\begin{enumerate}
 \item To be eligible, a job needs to be able to come back on the switch at the current clock (if clock = 0, take the first message able to come back).
 \item Between the eligible jobs, schedule first the one which has the lowest deadline.
 \item Repeat until all the messages had been scheduled.
\end{enumerate}

For any route i, the deadline correspond to $m_{s_i} + T_{max}$.

@@

	\paragraph{Analysis}
